Finite element analysis of multi-dimensional and simplified models for beams

### 2024-04-19 final_seminar/main.tex
conclusion

\section{Conclusion}
    \begin{frame}{Conclusion}
        \begin{itemize}
            \item 
        \end{itemize}

        \textbf{Future Work:}
        \begin{itemize}
            \item Include damping in the models.
        \end{itemize}

>>>>

\section{Conclusion}
    \begin{frame}{Conclusion}
        \textbf{What we have done:}
        \begin{itemize}
            \item Literature study on two articles.
            \item Presented three different models for a beam, each a different dimension.
            \item Looked at the well-posedness of the models.
            \item Looked into Modal Analysis, which forms the basis of the comparisons.
            \item Quickly discussed the Finite Element Method.
            \item Looked at the validity of the Timoshenko beam model. Part of the literature study.
            \item Extended the investigation to the validity of the two-dimensional beam model.
        \end{itemize}

        \textbf{Conclusion}
        \begin{itemize}
            \item We verified the results of the article.
            \item Shown that the Timoshenko cantilever beam model is a good approximation to the two-dimensional cantilever beam. The shape is important.
            \item Shown that the two-dimensional cantilever beam is a good approximation to the three-dimensional cantilever beam.
            \item The shape of the beams are very important to how well the models compare.
            \item Showed results for various shapes, that can be considered realistic for practical applications of a beam.
        \end{itemize}

        \textbf{Future Work:}
        \begin{itemize}
            \item Include damping in the models.
            \item Expand to plate models (this is done in my masters)
            \item Investigate the effect of different distrubances on the models.
        \end{itemize}
